
\subsection{College is among the best time for Chinese students to learn music}
On the one hand, for Chinese middle school students, it becomes slightly impossible to learn something extra because their schedules are becoming tighter and tighter these days. The figure shows a regular timetable for Chinese middle school students. Under the pressure of entering a so-called good university, they have to work harder and harder. For primary school students, they are basically forced to learn something like the piano by their parents in order to gain extra grades in Gaokao. However, in 2008, the national educational administration had declared the cancellation of the extra grades policy, which discourage students from learning the piano or something like that. \par
On the other hand, as is showed in Music for Relaxation: A Comparison Across Two Age Group, older adults seem less sensitive to emotional expressions in music than younger adults. Below is the comparison table. Different age adults respond to music certain music to different extend. Besides, college students bear strong emotional inspirations and learn new things easily as their concentration is better than older adults. Combining college students’ better sensitivity and higher concentration level, it is more suitable to learn music in college than in the later stage.\par
In conclusion, college is one of the best periods to learn music since it is a little bit impossible to learn in the later stage and worse to learn in the later stage.
Music can inspire creativity

