\documentclass[titlepage,a4paper,12pt]{article}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{float}
\hypersetup{
            hypertex=true,
            colorlinks=true,
            linkcolor=blue,
            anchorcolor=blue,
            citecolor=blue}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\bfseries{}Yang \thepage}
\begin{document}
    %\textrm{Roman Family}
    \title{Should music be encouraged as electives for engineering students?}
    \author{Zeyu Yang}
    \date{\today}
    \maketitle
    \tableofcontents
    \listoffigures
    
    \textbf{Abstract}: Engineering schools are among the most popular colleges. Some of them like UM-SJTU JI are fond of interdisciplinarity. But should interdisciplinary just be applied within the realm of 
engineering? Many engineering students like music, should they be given the right to have professional 
music training opportunities in their own college? This paper is produced for the necessity of offering 
music courses in engineering school. Articles from reliable databases and some survey results done by the 
author are the main evidences. The main focuses are costs, music therapy and so on. The conclusion is
that engineering schools should encourage students to take music courses by actually offering them, but
they cannot be so strict with the GPA concerning to musical courses.
    \input{introduction.tex}
    \input{AFTA.tex}
    \input{AFTO.tex}
    \input{MyPosition.tex}
    \input{Conclusion.tex}
    



    \begin{appendix}
        Here is all the reference.
    \end{appendix}
\end{document}
